---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

# Reproducible Research: Peer Assessment 1



## Loading and preprocessing the data

Read the CSV data from the raw file:
```{r}
data <- read.csv("activity.csv")
```


## What is mean total number of steps taken per day?

Use the tapply function to get the total number of steps for each day: 
```{r}
StepsPerDay <- tapply(data$steps, data$date, sum)
```


Calculate the mean steps using the mean function, and setting na.rm = TRUE to exclude any "NA" values:
```{r}
MeanStepsPerDay <- mean(StepsPerDay, na.rm = TRUE)
```

The resulting mean is `r MeanStepsPerDay`. 


Calculate the median steps using the medain function, and setting na.rm = TRUE to exclude any "NA" values:
```{r}
MedianStepsPerDay <- median(StepsPerDay, na.rm = TRUE)
```

The resulting median is `r MedianStepsPerDay`. 
    
  
Totally ran out of time to do the rest.... Thanks for marking!  
  

## What is the average daily activity pattern?






## Imputing missing values






## Are there differences in activity patterns between weekdays and weekends?






